Hybrid platforms and bargaining power

### 2023-04-05 src/paper/application.tex
Update graph x limits

Owing to the additive nature of the total profit function, an even stronger result can be established.
Notice that $f$ has the functional form required for proposition \ref{prop:aggregate_size_additive} with $g(x) = \frac{x}{1+x}, \alpha = V_P, \beta = V_F$.
Therefore, the same proposition implies that
\begin{align*}
    \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F},
\end{align*}
that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).\footnote{
    The intuition behind this is demonstrated in \cref{fig:F_F_eq}.
    As the platform's product variety grows, its bargaining power also increases.
    This can be thought of as an increase in (implied) entry fees, which in turn discourages fringe entry.
}
Conversely, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
    The same result also holds true for an increase in $V_P$.
}
As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:aggregate_eq}).
Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
    Unless $V_P N_P$ is high enough that the platform would operate in pure retail mode in the benchmark model, too.
}
\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$N_F^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=1.4, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty
            ]
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=N_F_bench]{\equilibrium};
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=N_F]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=N_F_cf]{\equilibrium};
            \legend{Benchmark, Bargaining, Fixed aggregate}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium number of fringe firms as a function of the number of platform products.}
    \label{fig:fringe_entry_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$A^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=2.6, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=south east
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=A_bench]{\equilibrium};
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=A]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A_noF]{\equilibrium};
            \legend{Benchmark, Bargaining, Pure retail}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium aggregate as a function of the number of platform products. Note, that consumer surplus is monotone in the aggregate, therefore this figure also shows ordinal changes in the equilibrium consumer surplus.}
    \label{fig:aggregate_eq}
\end{figure}

>>>>

Owing to the additive nature of the total profit function, an even stronger result can be established.
Notice that $f$ has the functional form required for proposition \ref{prop:aggregate_size_additive} with $g(x) = \frac{x}{1+x}, \alpha = V_P, \beta = V_F$.
Therefore, the same proposition implies that
\begin{align*}
    \frac{\partial N_F^*}{\partial N_P} < -\frac{V_P}{V_F},
\end{align*}
that is, an increase in the platform's products leads to a more than proportional reduction in the number of fringe products (\cref{fig:fringe_entry_eq}).\footnote{
    The intuition behind this is demonstrated in \cref{fig:F_F_eq}.
    As the platform's product variety grows, its bargaining power also increases.
    This can be thought of as an increase in (implied) entry fees, which in turn discourages fringe entry.
}
Conversely, equilibrium total aggregate is also decreasing in $N_P$.\footnote{
    The same result also holds true for an increase in $V_P$.
}
As, in this model, consumer welfare is monotone in the total aggregate, this implies that consumer welfare is decreasing in the number of the platform's products (\cref{fig:aggregate_eq}).
Therefore, as opposed to the benchmark model, the platform becoming more hybrid leads to a reduction in consumer welfare.\footnote{
    Unless $V_P N_P$ is high enough that the platform would operate in pure retail mode in the benchmark model, too.
}
\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$N_F^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=1.4, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty
            ]
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=N_F_bench]{\equilibrium};
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=N_F]{\equilibrium};
            \addplot[color=black,mark=none,thick,dotted] table[x=N_P,y=N_F_cf]{\equilibrium};
            \legend{Benchmark, Bargaining, Fixed aggregate}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium number of fringe firms as a function of the number of platform products.}
    \label{fig:fringe_entry_eq}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
                xlabel={$N_P$},
                ylabel={$A^*$},
                xmin=0, xmax=1.5, % adjust these values as needed
                ymin=0, ymax=3, % adjust these values as needed
                width=10cm, % adjust the width of the plot
                height=6cm, % adjust the height of the plot
                axis lines=left,
                xtick=\empty, ytick=\empty,
                legend pos=south east
            ]
            \addplot[color=blue,mark=none,very thick] table[x=N_P,y=A_bench]{\equilibrium};
            \addplot[color=red,mark=none,very thick] table[x=N_P,y=A]{\equilibrium};
            \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A_noF]{\equilibrium};
            \legend{Benchmark, Bargaining, Pure retail}
        \end{axis}
    \end{tikzpicture}
    \caption{Equilibrium aggregate as a function of the number of platform products. Note, that consumer surplus is monotone in the aggregate, therefore this figure also shows ordinal changes in the equilibrium consumer surplus.}
    \label{fig:aggregate_eq}
\end{figure}
